---
title: "Practical Machine Learning Course Project"
author: "Shreya Bansal"
date: "24 October 2020"
output:
  html_document: default
  word_document: default
---
Introduction

I have made a project for the PML course using knitr and rstudio markdown.

A brief overview

I collected many databases from different bands for the purpose of analysing them for this project.

Here, with the data from the acclmtr measure of the individuals of their respective classes of physical activity with the help of data, I predicted if a person is carrying out the exercises properly or not and the 2 files include both the test and training datasets, and from this I predicted the numbering pattern.
I am loading data for the processing of the data & then I performed the main decomposition and then prediction for which model to finalise.


```{r}
library(caret)
library(knitr)

library(data.table)
library(rpart.plot)
library(rpart)

library(gbm)
library(ggplot2)

library(corrplot)

```
Clean and perform Exploratory Analysis.

```{r}
t_url_ <- "https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv"
tr___URL  <- "https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv"

d___tst <- read.csv(url(t_url_))
d_____TRAAA <- read.csv(url(tr___URL))


```
Clean input of data

```{r}
training___data <- d_____TRAAA[, colSums(is.na(d_____TRAAA)) == 0]
testing___data <- d___tst[, colSums(is.na(d___tst)) == 0]
```
Prep all data for predcn., consider 70 percent of  data for that training set and remaining for testing data set
& use testing_data for the prediction of the 20 cases...

```{r}
training___data <- training___data[, -c(1:7)]
testing___data <- testing___data[, -c(1:7)]
dim(training___data)
```

```{r}
set.seed(1234)
da_ta__trng <- createDataPartition(d_____TRAAA$classe, p = 0.7, list = FALSE)
training___data <- training___data[da_ta__trng, ]
testing___data <- training___data[-da_ta__trng, ]
dim(training___data)
dim(testing___data)
```
Next step is
```{r}
noneZero <- nearZeroVar(training___data)
training___data <- training___data[, -noneZero]
testing___data <- testing___data[, -noneZero]
dim(training___data)
dim(testing___data)
```


```{r}
pc <- cor(training___data[, -53])
corrplot(pc, order = "FPC", method = "color", type = "upper", tl.cex = 0.8, tl.col = rgb(0, 0, 0))
```


I proceeded for model building using 2 algos...

```{r}
set.seed(20000)
trdc <- rpart(classe ~ ., data=training___data, method = "class")
rpart.plot(trdc)
```

Validate... 
```{r}
mpreee <- predict(trdc, testing___data, type = "class")
ab <- confusionMatrix(mpreee, testing___data$classe)
ab
```

```{r}
plot(mpreee)
```

APPLY 2 models

```{r}
set.seed(10000)
c_G_B_M <- trainControl(method = "repeatedcv", number = 5, repeats = 1)
V_G_B_M <- train(classe ~ .,data=training___data, method = "gbm", trControl = c_G_B_M, verbose = FALSE)
V_G_B_M$finalModel
```

THE PROJECT IS COMPLETE, THANKS.
